Basic MODIS preparation in GRASS GIS

### 2011-01-04 tutorials/grass_modis/article_GIPE.tex
updated i.modis.qc section
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44852 15284696-431f-4ddb-bdfa-cd5b030d7da7

\section{QA Flags screening}
Use the \textit{i.modis.qc} module.

@@

>>>>

\section{QA Flags screening}
Use the \textit{i.modis.qc} module with MODIS Vegetation products (i.e. MOD13A2) as shown in the screenshot below:
\begin{smallverbatim}
MOD13A2: Mandatory QA Flags 1Km bits[0-1]
* [00]= class 0: VI produced, good quality
* [01]= class 1: VI produced, but check other QA
* [10]= class 2: Pixel produced, but most probably cloud
* [11]= class 3: Pixel not produced due to other \
    reasons than clouds
\end{smallverbatim}

@@

If you want to use shell scripting, the example below shows how to process Quality Assessment for Land Surface Temperature (i.e. MOD11A1):
\begin{smallverbatim}

MOD11A1: Mandatory QA Flags bits=[0-1]
* [00]= class 0: LST produced, good quality, \
    not necessary to examine more detailed QA
* [01]= class 1: LST produced, other quality, \
    recommend examination of more detailed QA
* [10]= class 2: LST not produced due to cloud effects
* [11]= class 3: LST not produced primarily due \
    to reasons other than cloud

for QC in mandatory_qa_11A1 data_quality_flag_11A1 \
 emis_error_11A1 lst_error_11A1
 do
 i.modis.qc productname=mod11A1 qcname=$QC \
 input=mod11A1.QC out=mod11A1_$QC
done
\end{smallverbatim}
